---
title: "Presentation"
author: "Ziping, Ole, Kristian"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tidy Friday

Team Tornado

Citation: Tidy Tuesday: <https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-05-16/readme.md>

## Load libraries

```{r include=FALSE}
library(tidyverse)
library(mapdata)
```

## Load data

```{r cars, include=FALSE}
tornados <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-16/tornados.csv')
```

## Questions

-   How many tornadoes occur each year

-   Where do tornadoes occur most often? Map

-   Does the number of tornadoes pr year change between 1950 - 2022

-   Does the magnitude of tornadoes change between 1950 - 2022.

-   Does the number of injuries/fatalities correlate with the magnitude for entire time-period?

    -   If accounting for loss (\$) remember to account for inflation

-   Can you predict the number of injuries/fatalities/losses based on position (state), year, magnitude, width, length, number of states affected

You can also embed plots, for example:

```{r pressure, echo=FALSE} plot(pressure)}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
